%-------------------------
% Resume in Latex
% Author : Suhaib Khan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBold}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListHeading}[1]{\textbf{#1}\vspace{-5pt}}

%------------------------------------------- 
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://suheb.in/}{\Large Suhaib Khan}} London, SE167EW & Email : \href{mailto:suheb.work@gmail.com}{suheb.work@gmail.com}\\
  \href{https://suheb.in/}{Web://suheb.in } \textbar \href{https://github.com/suheb}{ Github://suheb} \textbar \href{https://www.linkedin.com/in/suhebk/}{ LinkedIn://suhebk} & Mobile: +447375831534
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {\href{https://www.pwc.co.uk}{\underline{PwC}}}{London, UK}
      {Software Engineer (Contractor)}{Oct 2019 - Present}
      \resumeItemListStart
          \resumeItemNoBold
          {Built a search microservice with \textbf{ElasticSearch}  using Falcon (\textbf{Python} framework).}
          \resumeItemNoBold
          {Worked on setting up the project infrastructure as code using \textbf{Terraform}.}
           \resumeItemNoBold
          {Lead and maintained the deployment of various microservices on GCP using \textbf{Kubernertes} engine}
          \resumeItemNoBold
          {Added token-based authorisation to microservices using \textbf{Keycloak} as the authorisation provider.}
          \resumeItemNoBold
          {Worked on building a \textbf{Python} framework that drastically reduces the time to setup new microservices.}
          \resumeItemNoBold
          {Maintained the frontend code of the application written in \textbf{React} by a third-party agency.}
      \resumeItemListEnd
   \resumeSubheading
   	  {\href{https://picnic.app/}{\underline{Picnic}}}{Amsterdam, NL}
      {Software Engineer}{Oct 2018 - Aug 2019}
      \resumeItemListStart
          \resumeItemNoBold
          {Built the cross-platform app in \textbf{React Native} used by the entire delivery fleet for making deliveries to customers.}
          \resumeItemNoBold
          {Created a web dashboard in \textbf{React} with a overview of all deliveries and real-time location of delivery persons.}
          \resumeItemNoBold
          {Used \textbf{TypeScript} for static type safety and built a decoder generator for run-time type safety.}
           \resumeItemNoBold
          {Worked on the deployment strategy for the web application using \textbf{Kubernetes} on AWS}
          \resumeItemNoBold
          {Mentored an intern from a coding bootcamp and groomed him into a professional developer.}
      \resumeItemListEnd
      
    \resumeSubheading
   	  {\href{https://www.microsoft.com}{\underline{Microsoft}}}{Bangalore, IN}
      {Software Engineer}{July 2018 - Sept 2018}
      \resumeItemListStart
          \resumeItemNoBold
          {Part of the team working on migrating Microsoft Teams to \textbf{React} from AngularJS.}
          \resumeItemNoBold
          {Built a side-by-side search result comparison tool for Microsoft Teams in \textbf{AngularJS}}
          \resumeItemNoBold
          {Added analytics that allowed the team to measure the performance of the new search API}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.zomato.com}{\underline{Zomato}}}{Gurgaon, IN}
      {Software Development Engineer}{Oct 2016 - June 2018}
      
      \resumeItemListHeading{Zomato Base (Point of Sale (POS) system for restaurants)}
      \resumeItemListStart
          \resumeItemNoBold
          {Built a prototype for a web-based version of the POS system using \textbf{React} for smaller businesses.}
          \resumeItemNoBold
          {Worked on the web dashboard built with \textbf{Laravel} and \textbf{jQuery} for restaurant owners to manage their outlets.}
          \resumeItemNoBold
          {Built the page templates using \textbf{Blade} templating engine with \textbf{HTML5} and \textbf{CSS3}.}
           \resumeItemNoBold
          {Built a \textbf{MongoDB} based logging system for monitoring user's journey and actions on the dashboard.}
        %   \resumeItemNoBold
        %   {Developed menu management system to manage multiple outlets efficiently from a centralized dashboard.}
        %   \resumeItemNoBold
        %   {Created combo management system with automated pricing for products based on their original price.}
        %   \resumeItemNoBold
        %   {Worked on the inventory management with automatic stock reduction based on predefined recipes.}
          \resumeItemNoBold
          {Added caching layer to the user permission module using \textbf{Redis} to improve page load time by 50\%.}
      \resumeItemListEnd
      
      \resumeItemListHeading{Zomato Cashless (Order using Zomato app at Dine In restaurants)}
      \resumeItemListStart
          \resumeItemNoBold
          {Integrated the Zomato consumer app with the POS system that allows users to order from their own phone.}
        %   \resumeItemNoBold
        %   {Built a two-way data flow system that allows changes to order from both the app and the POS system.}
          \resumeItemNoBold
          {Built the APIs to create/update order from the app and push the data to POS system using \textbf{PubNub}.}
          \resumeItemNoBold
          {Created \textbf{webhooks} to provide order status updates to app and push changes from POS system to the app.}
      \resumeItemListEnd
      
      \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/archive/2017/projects/6041859612737536/}{\underline{Google Summer of Code 2017}}}{Remote}
      {\href{http://cltk.org/}{Mentor, Classical Language Toolkit (CLTK)}}{April 2017 - Sept 2017}
      \resumeItemListStart
          \resumeItemNoBold
          {Mentored the project to build an annotations module for CLTK webapp.}
          \resumeItemNoBold
          {Worked closely with the student and the other mentor to design a modular system.}
      \resumeItemListEnd
      
	\resumeSubheading
      {\href{https://archimedes.digital}{\underline{Archimedes Digital}}}{Remote}
      {Web Developer}{Aug 2016 - Sept 2016}
      \resumeItemListStart
        \resumeItemNoBold
          {Worked on developing an online catalog for museums using scans of various objects using \textbf{React}.}
        \resumeItemNoBold
          {Developed a highly zoomable image viewer to high-resolution scans in detail.}
        \resumeItemNoBold
          {Integrated \textbf{code linting} and setup \textbf{test suites} to be used across projects.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/archive/2016/projects/6243113458728960/}{\underline{Google Summer of Code 2016}}}{Remote}
      {\href{http://cltk.org/}{Classical Language Toolkit (CLTK)}}{May 2016 - Sept 2016}
      \resumeItemListStart
          \resumeItemNoBold
          {Built the CLTK webapp in \textbf{React} - a modern reading environment to study classical languages.}
          \resumeItemNoBold
          {Created a REST API for CRUD operations using \textbf{Python} and \textbf{Flask}}
          \resumeItemNoBold
          {Updated the webapp to provide definitions, translations and commentary along with the text.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://www.aspiringminds.com}{\underline{Aspiring Minds}}}{Gurgaon, IN}
      {Research and Development Intern}{June 2015 - July 2015}
      \resumeItemListStart
        \resumeItemNoBold
          {Developed a CRM-simulation module integrated into the employability assessment platform AMCAT.}
        \resumeItemNoBold
          {Built the UI for the module from scratch and built the backend for question delivery and scoring.}
        \resumeItemNoBold
          {Designed the database schema for the module compatible with the current platform’s database.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/suheb/musichub}{\underline{Music Hub}}}
      {Android app that connects multiple devices via WIFI and plays music in all connected devices simultaneously to create a loud stereo-like sound effect.}
    \resumeSubItem{\href{https://play\underline{.google.com/}store/apps/details?id=com.haloappstudio.musictimer&hl=en}{\underline{Music Timer}}}
      {Android app that monitors phone’s movement to detect whether the user is asleep and pause music playback accordingly.}
  \resumeSubHeadingListEnd

%--------OPEN SOURCE------------
\section{Open Source Contributions}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/cltk}{\underline{CLTK}}}
      {Active member, worked on the \href{https://github.com/cltk/cltk_frontend/commits?author=suheb}{\underline{CLTK Web app}} and \href{https://github.com/cltk/cltk_api/commits?author=suheb}{\underline{CLTK API}}.}
    \resumeSubItem{\href{https://github.com/fossasia}{\underline{FOSSASIA}}}
      {Past contributor, worked on the Open Event project (both \href{https://github.com/fossasia/open-event-server/pulls?q=is\%3Apr+author\%3Asuheb+is\%3Aclosed}{\underline{Server}} and \href{https://github.com/fossasia/open-event-droidgen/pulls?q=is\%3Apr+is\%3Aclosed+author\%3Asuheb}{\underline{Android app}}).}
    \resumeSubItem{\href{https://github.com/phpbb}{\underline{phpBB}}}
      {Past contributor, implemented a live search \href{https://github.com/phpbb/phpbb/pulls?q=is\%3Apr+author\%3Asuheb+is\%3Aclosed}{\underline{feature and fixed bugs}}.}
  \resumeSubHeadingListEnd
  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
       {Javascript, TypeScript, Python, Java, C++, PHP, SQL, HTML, CSS}
    \resumeSubItem{Tools and Frameworks}
       {React, React Native, jQuery, Flask, Git, Android, Laravel, MySQL}
 \resumeSubHeadingListEnd

%--------AWARDS and ACHIEVEMENTS------------
\section{Awards and Achievements}
  \resumeSubHeadingListStart
    % \resumeSubItem{Google Summer of Code 2016}
    %   {Selected as a student to work under Classical Language Toolkit.}
    \resumeSubItem{Hack @ NSIT 2016}
       {1st Prize, developed an app to collect authenticated survey data using Iris Scanner.}
    \resumeSubItem{Androidathon 2014}
       {2nd Prize, developed an app to connect servicemen to households.}
  \resumeSubHeadingListEnd
%-------------------------------------------


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Netaji Subhas Institute of Technology}{New Delhi, India}
      {Bachelor of Engineering in Information Technology}{Aug. 2012 -- May. 2016}
  \resumeSubHeadingListEnd


%--------TALKS & CONFERENCES------------
\section{Talks and Conferences}
 \resumeSubHeadingListStart
    \resumeSubItem{\href{https://2017.fossasia.org/tracks.html\#2891}{\underline{FOSSASIA Summit 2017}}}{Introduction to the Classical Language Toolkit and Archive}\hfill{Singapore}
    \resumeSubItem{\href{https://github.com/linuxchixin/talks}{\underline{LinuxChix India Meetup}}}
       {How SSH Works?}\hfill{New Delhi}
    \resumeSubItem{\href{https://www.meetup.com/pydelhi/events/mglhqpyxhbqb/}{\underline{PyDelhi}}}
       {Dabbling with Decorators}\hfill{New Delhi}
 \resumeSubHeadingListEnd
\end{document}